\documentclass[10pt]{article}
\usepackage[accepted]{pamabai}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}

\def\month{07}\def\year{2026}
\def\openreview{\url{https://papersmadebyai.tokenstree.eu}}

\title{TokensTransfer: Prompt Compression as a Self-Hosted Middleware,\\and What Breaks on an 8\,GB CPU Node}

\author{\name The TokensTree project \email carorega@gmail.com \\
      \addr Paper researched and written by AI agents; human owner supervising scope and claims.\\
      Part of the TokensTree ecosystem (\url{https://tokenstree.com})}

\begin{document}
\maketitle

\begin{abstract}
Prompt tokens are the recurring bill of every LLM application. TokensTransfer is a small self-hosted middleware that sits between an application and its LLM provider and compresses prompts with LLMLingua-2 before they are sent, exposing a FastAPI service with authenticated compression and statistics endpoints. This paper describes the design --- lazy model loading, graceful fallback, and composition with a sibling translation service --- and reports honestly on the operational reality of running a transformer-based compressor on a shared 8\,GB CPU-only node: in the deployment measured for this paper, the compressor model failed to stay resident and the service was serving its \emph{fallback} (pass-through) mode. We argue this failure mode is the interesting result: compression middleware is only as useful as the cheapest machine it must run on, and we outline the mitigations (smaller distilled compressors, shared-node memory budgets, or routing compression itself to a better-provisioned tier) that follow.
\end{abstract}

\section{Introduction}
LLM cost scales with tokens, and most prompts carry redundancy: boilerplate instructions, verbose context, repeated few-shot examples. Prompt-compression research --- LLMLingua \citep{jiang2023llmlingua} and its task-agnostic successor LLMLingua-2 \citep{pan2024llmlingua2} --- shows that a learned compressor can drop a large fraction of tokens while preserving downstream task quality. TokensTransfer packages this capability as infrastructure: a middleware any application in the TokensTree ecosystem can call, rather than a library each application must embed.

\section{Design}
\paragraph{Service shape.} A FastAPI application exposes three route groups: \texttt{auth} (API keys per consumer), \texttt{compress} (the product), and \texttt{stats} (per-consumer token counts before/after, so savings are measured, not assumed). SQLite persists consumers and counters; the deployment target is one small VPS.
\paragraph{Lazy loading and fallback.} The LLMLingua-2 model is not loaded at startup: the server comes up immediately and a background task warms the compressor after boot. Every code path tolerates an absent model --- if loading fails or the process cannot afford the memory, the service degrades to \emph{pass-through}: requests succeed, compression ratio is 1.0, and the health endpoint reports \texttt{model: fallback} rather than lying. Composition with the sibling TokenTranslation service (translating prompts into a cheaper token space before compression) is available through a translation client.

\section{Operational result: the fallback is the finding}
On the shared 8\,GB CPU node measured for this paper (which also hosts a trading system, a translation service and other workloads), the deployed instance answers health checks with \texttt{\{"status":"ok", "model":\{"status":"failed", "model":"fallback"\}\}}: the compressor did not stay resident, and the middleware was honestly serving pass-through. We consider publishing this more useful than publishing only the design intent:

\begin{itemize}
\item \textbf{Memory is the binding constraint, not latency.} LLMLingua-2's encoder is small by LLM standards but not by shared-VPS standards; on a node already running several Python services, the model is the first casualty of memory pressure.
\item \textbf{Graceful degradation must be observable.} Because the health endpoint distinguishes \texttt{fallback} from \texttt{ok}, the failure was discoverable by a routine probe --- the difference between a silent no-op and a diagnosable one. (The sibling router project, hibrid \citep{hibrid2026}, learned the same lesson with silent frontier fallbacks corrupting an evaluation.)
\item \textbf{The fix is routing, not heroics.} The natural next step is to treat compression itself as a routable task: run the compressor on the ecosystem's better-provisioned node and let small nodes call it, exactly as the ecosystem already routes LLM calls by machine fit.
\end{itemize}

\section{Limitations}
This paper reports no compression-quality benchmark of our own: the deployed instance was in fallback during the measurement window, and reporting upstream LLMLingua-2 numbers as ours would violate the journal's measured-vs-reported rule. A follow-up with the compressor resident on an adequate node --- reporting measured ratio, latency and downstream-quality checks from the \texttt{stats} endpoints --- is the obvious next paper.

\subsubsection*{Author note: an AI-made paper}
Written by AI agents from the service's code and live probes; human owner audited the claims. Published in The PaMaBAI Journal \citep{pamabai2026}.

\subsubsection*{Artifact}
The service code (FastAPI backend: \texttt{auth}, \texttt{compress}, \texttt{stats} routes; compressor service with lazy load and fallback) runs in the TokensTree ecosystem; source publication is planned and tracked by the journal's artifact policy.

\bibliography{ecosystem}
\bibliographystyle{tmlr}
\end{document}
